Death By Dropdown?

### 2025-04-01 conference-materials/2025_shiny-conf/slides.qmd
Updates visuals and layout in slides
- Replaces slide 4 image file and updates CSS references to improve visual consistency.
- Adjusts layout for better content
presentation on slides 4 and 5.

## BID In Action: Dashboard Transformation {.center background-color="#F0F0F0"}

::: {.fragment}
<!-- TODO: exchange for gif -->
![](img/before-bid.png)
:::

@@

![](img/bid-framework.png)

:::: {.columns}
::: {.column width="45%"}
1. **Notice** the Problem
2. **Interpret** the User's Need
3. **Structure** the Dashboard
:::

::: {.column width="45%"}
4. **Anticipate** User Behavior
5. **Validate** & Empower the User
::: 
::::

@@

## Where BID Fits In {background-color="#F0F0F0"}

>>>>

## BID In Action: Dashboard Transformation {.center background-color="#F2F2F2"}

::: {.absolute top="80%" left="12%" width="80%"}
<!-- TODO: exchange for gif -->
![](img/before-bid.png)
:::

@@

::: {.absolute left="7%" width="90%"}
![](img/bid-framework.png)
:::

:::: {.columns .absolute top="58%"}

::: {.column width="27%"}
1. **Notice** the Problem
:::

::: {.column width="46%"}
2. **Interpret** the User's Need
3. **Structure** the Dashboard
4. **Anticipate** User Behavior
:::

::: {.column width="27%"}
5. **Validate** & Empower the User
:::

::::

@@

## Where BID Fits In {background-color="#F2F2F2"}
